Innovation and elaboration on the avian tree of life - supplementary materials

### 2023-06-01 Manuscript/supplementaries.tex
results discussion done!

@@

\begin{figure}[htpb]
\centering
   \includegraphics[width=0.9\textwidth]{Figures/correlations_fable.pdf}
\caption{Posterior distributions of the correlations scores between $elaboration_{species}$ and $innovation_{species}$ as displayed for each super-orders in Fig. \ref{Fig:figure_correlations}. Species' projection onto the whole phylogeny's major axis of phenotypic variance-covariance (VCV) corresponds to the correlation scores for the panels A and B in Fig. \ref{Fig:figure_correlations} and species' projections onto their own super-order's major axis of phenotypic variance-covariance (VCV) corresponds to the correlation scores for the panel C in Fig. \ref{Fig:figure_correlations}.}
\label{Fig:fable_correlations}
\end{figure}

>>>>

\begin{figure}[htbp]
\centering
   \includegraphics[width=0.7\textwidth]{Figures/InnovElabTree_supp_revision.pdf}
\caption{Avian phylogeny (n = 8748 species) showing distributions of species beak shape $elaboration_{species}$ (inner circle, yellow scale), $innovation_{species}$ (outer circle, blue scale), and Euclidean distance of species to the centroid of beak space (branches, cividis scale).}
\label{Fig:phylogeny_supplement}
\end{figure}

@@

\begin{figure}[htpb]
\centering
   \includegraphics[width=0.9\textwidth]{Figures/correlations_fable.pdf}
\caption{Posterior distributions of the correlations scores between $elaboration_{species}$ and $innovation_{species}$ as displayed for each super-orders in Fig. \ref{Fig:figure_correlations}. Species' projection onto the whole phylogeny's major axis of phenotypic variance-covariance (VCV) corresponds to the correlation scores for the panels A and B in Fig. \ref{Fig:figure_correlations} and species' projections onto their own super-order's major axis of phenotypic variance-covariance (VCV) corresponds to the correlation scores for the panel C in Fig. \ref{Fig:figure_correlations}.}
\label{fable_correlations_supplementary}
\end{figure}
